---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# reuse

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/maurolepore/reuse/branch/main/graph/badge.svg)](https://app.codecov.io/gh/maurolepore/reuse?branch=main)
<!-- badges: end -->

The goal of reuse is to avoid re-running slow computations, particularly in
pipes. 

`reuse::reuse()` combines features of `pins::pin_read()` and `pins::pin_write()`
but:

* can be used anywhere in a pipe, 
* defaults to using a cache directory appropriate for your system,
* can update the cache for one object or an entire R session.


Main features:

* Can be used anywhere in a pipe.
* can update objects with the argument `update` or the global option
`reuse.update`.
* can set a cache "board" (folder) with the global option `reuse.board`.

## Installation

You can install the development version of reuse like so:

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/reuse")
```

## Example

```{r example}
library(reuse)
```

* Is plays well with the pipe.
* It saves computations, reusing the cache if possible.

```{r}
one <- 1 %>% reuse("one")
two <- 2 %>% reuse("one")
two
```

* You can update the cache for one call with the argument `update`.

```{r}
two <- 2 %>% reuse("one", update = TRUE)
two
```

* You can update the cache for one session with the option `reuse.update`.

```{r}
options(reuse.update = TRUE)

three <- 3 %>% reuse("one")
three
```

* The default cache folder uses the appropriate directory for Linux, Mac, and
Windows, via the [rappdirs](https://rappdirs.r-lib.org/) package.

```{r}
cache_dir <- rappdirs::user_cache_dir("reuse")
dir.exists(file.path(cache_dir, "one"))
```

* It's based on the [pins](https://pins.rstudio.com/) package, which you can
use to manage your cache folder a.k.a. "board".

```{r}
library(pins)

board <- board_folder(cache_dir)
board %>% pin_meta("one")

board %>% pin_delete("one")
```

* You can use a custom cache folder with the argument `board`.

```{r}
custom <- pins::board_folder(tempdir())
1 %>% reuse("abc", board = custom)

pins::pin_read(board = custom, "abc")
```

* You can use a custom cache folder with the option `reuse.board`.

```{r}
options(reuse.board = custom)
1 %>% reuse("def", board = custom)

pins::pin_exists(board = custom, "def")
```
