---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# reuse

<!-- badges: start -->
<!-- badges: end -->

The goal of reuse is to reuse R objects.

## Installation

You can install the development version of reuse like so:

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/reuse")
```

## Example

```{r example}
library(reuse)
```

* Is pipable.
* It saves computations, reusing the cache if possible.

```{r}
one <- 1 %>% reuse("one")
two <- 2 %>% reuse("one")
two
```

* You can overwrite the cache for one call with the argument `overwrite`.

```{r}
two <- 2 %>% reuse("one", overwrite = TRUE)
two
```

* You can overwrite the cache for one session with the option `reuse.overwrite`.

```{r}
options(reuse.overwrite = TRUE)

three <- 3 %>% reuse("one")
three
```

* By default it uses the appropriate directory for Linux, Mac, and Windows, via
the [rappdirs](https://rappdirs.r-lib.org/) package.

```{r}
cache_dir <- rappdirs::user_cache_dir("reuse")
list.files(cache_dir)
```

* It's based on the [pins](https://pins.rstudio.com/) package, which you can
use to manage your cached objects.

```{r}
library(pins)
pin_delete(board = board_folder(cache_dir), names = "one")
list.files(cache_dir)
```
